Geometric signs reveal changes in social structures and networks during the Western Eurasian Aurignacian

### 2025-06-09 paper/paper.qmd
update citation style to NHB

---
title: "Geometric signs reveal changes social structures and networks during the Western Eurasian Aurignacian"
author:
  - Sophie Cooper:
      institute: uw
      orcid: xxx
  - Ben Marwick:
      correspondence: "yes"
      email: bmarwick@uw.edu
      orcid: 0000-0001-7879-4531
      institute:
        - uw
institute:
  - uw: Department of Anthropology, University of Washington, Seattle, USA
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 1000
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/society-for-american-archaeology.csl" # Insert path for the bib-style
abstract: |
  ...
keywords: |

>>>>

---
title: "Geometric signs reveal changes in social structures and networks during the Western Eurasian Aurignacian"
author:
  - Sophie Cooper:
      institute: uw
      orcid: xxx
  - Aleah Rosner:
      institute: uw
      orcid: xxx
  - Eva Oryn:
      institute: uw
      orcid: xxx
  - Kenneth B. Vernon:
      orcid: 0000-0003-0098-5092
      institute:
        - uu
  - Ben Marwick:
      correspondence: "yes"
      email: bmarwick@uw.edu
      orcid: 0000-0001-7879-4531
      institute:
        - uw
institute:
  - uw: Department of Anthropology, University of Washington, Seattle, USA
  - uu: Scientific Computing and Imaging Institute, University of Utah, Salt Lake City, USA
title-block-published: "Last updated"  
date: now
date-format: long
format: 
  docx:
    reference-doc: "../templates/template.docx" # Insert path for the DOCX file
execute:
  echo: false
  warning: false
  message: false
  comment: "#>"
  fig-path: "../figures/"
  fig-dpi: 1000
filters:
  - ../templates/scholarly-metadata.lua
  - ../templates/author-info-blocks.lua
  - ../templates/pagebreak.lua
bibliography: references.bib
csl: "../templates/nature.csl" # Insert path for the bib-style
abstract: |
  ...
keywords: |
